Generating Random Logic Programs Using Constraint Programming

### 2020-07-25 talk/talk.tex
A few more slides

\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes}
\tikzstyle{every picture}+=[remember picture]

@@

\DeclareMathOperator{\ifff}{:-}
\DeclareMathOperator{\prob}{::}

@@

\begin{frame}{Probabilistic Logic Programs (\textsc{ProbLog})}
  \begin{block}{The Smokers Network (\cite{DBLP:conf/ilp/DomingosKLPRS08})}
    \vspace*{-\baselineskip}\setlength\belowdisplayshortskip{0pt}
    \begin{align*}
      \textcolor{probability}{0.2} \prob &\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
      \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}) \ifff \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}). \\
      \textcolor{probability}{0.1} \prob &\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
      \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
                                         &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}). \\
                                         &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}), \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{X}}). \\
                                         &\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}). \\
                                         &\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}). \\
                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{michelle}}). \\
                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{timothy}}). \\
                                         &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}}, \textcolor{constant}{\mathit{michelle}}).
    \end{align*}
  \end{block}
\end{frame}

\begin{frame}{Applications}
  \begin{columns}[b]
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{application1.png}
      {\small \cite{DBLP:conf/icra/MoldovanMOSR12}}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{application3.png}
      {\small \cite{DBLP:conf/ijcai/DriesKDBR17}}
    \end{column}
  \end{columns}
  \vfill
  \begin{columns}[b]
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{application2.png}
      {\small \cite{DBLP:conf/ilp/Corte-RealD017}}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{application4.png}
      {\small \cite{de2013phenetic}}
    \end{column}
  \end{columns}
\end{frame}

% TODO: finish the explanation
\begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
  \begin{description}
  \item[NNF] negation normal form
  \item[d-DNNF] deterministic decomposable negation normal form
  \item[BDD] binary decision diagrams
  \item[SDD] sentential decision diagrams
  \item[$k$-Best] ???
  \end{description}
\end{frame}

\begin{frame}{Example Diagrams for $C \land (A \lor \neg B)$}
  \vspace{-1em}
  % \begin{tikzpicture}
  %   \node[draw,circle] {$\land$}
  %   child {node[draw,rectangle] {$C$}}
  %   child {node[draw,circle] {$\lor$}
  %     child {node[draw,rectangle] {$A$}}
  %     child {node[draw,rectangle] {$\neg B$}
  %     }
  %   };
  % \end{tikzpicture}
  \begin{columns}[b]
    \begin{column}{0.33\textwidth}
      \begin{figure}
        \begin{tikzpicture}
          \node[draw,circle] (A) {$A$}
          child {edge from parent[draw=none]}
          child {node[draw,circle] (B) {$B$} edge from parent[dashed]
            child {node[draw,circle,solid] (C) {$C$} edge from parent[dashed]
              child {node[draw,rectangle,solid] {$1$} edge from parent[solid]}
              child {node[draw,rectangle,solid] (0) {$0$}}
            }
            child {edge from parent[draw=none]}
          };
          \draw (A) -- (C);
          \draw (B) -- (0);
        \end{tikzpicture}
        \caption{BDD}
      \end{figure}
    \end{column}
    \begin{column}{0.34\textwidth}
      \begin{figure}
        \begin{tikzpicture}
          \node[draw,circle] {$\land$}
          child {node[draw,circle] {$\lor$}
            child {node[draw,circle] (parent) {$\land$}
              child {node[draw,rectangle] {$B$}}
              child {edge from parent[draw=none]}
            }
            child {node[draw,circle] {$\land$}
              child {node[draw,circle] {$\lor$}
                child {node[draw,rectangle] (A) {$A$}}
                child {node[draw,rectangle] {$\neg A$}}
              }
              child {node[draw,rectangle] {$\neg B$}}
            }
          }
          child {node[draw,rectangle] {$C$}};
          \draw (parent) -- (A);
        \end{tikzpicture}
        \caption{d-DNNF}
      \end{figure}
    \end{column}
    \begin{column}{0.33\textwidth}
      \begin{figure}
        \begin{tikzpicture}
          \tikzset{
            mysplit/.style={
              draw,
              rectangle,
              rectangle split,
              rectangle split horizontal,
              rectangle split parts=2
            }
          }
          \node[draw,circle] {$1$}
          child {node[mysplit] (bullet) {
              \nodepart{one} $\neg A$
              \nodepart{two}
            }
            child {node[draw,circle] (3) {$3$} edge from parent[draw=none]
              child {node[mysplit] {
                  \nodepart{one} $\neg B$
                  \nodepart{two} $C$
                }
              }
              child {node[mysplit] {
                  \nodepart{one} $B$
                  \nodepart{two} $0$
                }
              }
            }
          }
          child {node[mysplit] {
              \nodepart{one} $A$
              \nodepart{two} $C$
            }};
          \draw[*-] let \p1 = (bullet.two), \p2 = (bullet.center) in ({\x1 + 2.5},{\y2 + 2}) -- (3);
        \end{tikzpicture}
        \caption{SDD}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{What Characterises a (Probabilistic) Logic Program?}
  \begin{columns}
    \hspace*{-0.7cm}\begin{column}{0.75\textwidth}
      \begin{empheq}[left =\onslide<6->{\color{color5}\empheqlbrace}]{equation}
        \begin{align*}
      \textcolor<5->{probability}{0.2} \prob &\textcolor<2->{predicate}{\mathtt{stress}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}). \\
      \textcolor<5->{probability}{0.3} \prob &\textcolor<2->{predicate}{\mathtt{influences}}(\textcolor<3->{variable}{\mathsf{P}_1}, \textcolor<3->{variable}{\mathsf{P}_2}) \ifff \textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<3->{variable}{\mathsf{P}_1}, \textcolor<3->{variable}{\mathsf{P}_2}). \\
      \textcolor<5->{probability}{0.1} \prob &\textcolor<2->{predicate}{\mathtt{cancer\_spont}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}). \\
      \textcolor<5->{probability}{0.3} \prob &\textcolor<2->{predicate}{\mathtt{cancer\_smoke}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{X}}) \ifff \textcolor<2->{predicate}{\mathtt{stress}}(\textcolor<3->{variable}{\mathsf{X}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{X}}) \ifff \textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{Y}}), \textcolor<2->{predicate}{\mathtt{influences}}(\textcolor<3->{variable}{\mathsf{Y}}, \textcolor<3->{variable}{\mathsf{X}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{cancer}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{cancer\_spont}}(\textcolor<3->{variable}{\mathsf{P}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{cancer}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \tikz \coordinate (start);\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{P}}), \textcolor<2->{predicate}{\mathtt{cancer\_smoke}}(\textcolor<3->{variable}{\mathsf{P}})\tikz \coordinate (end);. \\
                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{michelle}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{timothy}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<4->{constant}{\mathit{timothy}}, \textcolor<4->{constant}{\mathit{michelle}}).
        \end{align*}
      \end{empheq}
    \end{column}
    \begin{column}{0.25\textwidth}
      \begin{itemize}
      \item[\textcolor{predicate}{\textbullet}]<2-> predicates, arities
      \item[\textcolor{variable}{\textbullet}]<3-> variables
      \item[\textcolor{constant}{\textbullet}]<4-> constants
      \item[\textcolor{probability}{\textbullet}]<5-> probabilities
      \item[\textcolor{color5}{\textbullet}]<6-> length
      \item[\textcolor{color6}{\textbullet}]<7-> complexity
      \end{itemize}
    \end{column}
  \end{columns}
  \onslide<7->{
    \begin{tikzpicture}[overlay]
      \draw [decorate,decoration={brace,amplitude=10pt,mirror},color=color6] (start) -- (end);
    \end{tikzpicture}
  }
\end{frame}

% TODO: describe clauses as trees (showing an example of a clause)
% TODO: describe the rest of the model
% TODO: add a link to GitHub at the end

@@

>>>>

\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes}
\tikzstyle{every picture}+=[remember picture]

@@

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\DeclareMathOperator{\ifff}{:-}
\DeclareMathOperator{\prob}{::}
\DeclareMathOperator{\negg}{\backslash+}

@@

\begin{frame}{Probabilistic Logic Programs (\textsc{ProbLog})}
  \begin{block}{``Smokers'' (\cite{DBLP:conf/ilp/DomingosKLPRS08,DBLP:journals/tplp/FierensBRSGTJR15})}
    \vspace*{-\baselineskip}\setlength\belowdisplayshortskip{0pt}
    \begin{align*}
      \textcolor{probability}{0.2} \prob &\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
      \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}) \ifff \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}). \\
      \textcolor{probability}{0.1} \prob &\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
      \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
                                         &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}). \\
                                         &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}), \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{X}}). \\
                                         &\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}). \\
                                         &\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}). \\
                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{michelle}}). \\
                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{timothy}}). \\
                                         &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}}, \textcolor{constant}{\mathit{michelle}}).
    \end{align*}
  \end{block}
\end{frame}

\begin{frame}{Applications}
  \begin{columns}[b]
    \begin{column}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{application1.png}
      {\small \cite{DBLP:conf/icra/MoldovanMOSR12}}
    \end{column}
    \begin{column}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{application3.png}
      {\small \cite{DBLP:conf/ijcai/DriesKDBR17}}
    \end{column}
  \end{columns}
  \vfill
  \begin{columns}[b]
    \begin{column}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{application2.png}
      {\small \cite{DBLP:conf/ilp/Corte-RealD017}}
    \end{column}
    \begin{column}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{application4.png}
      {\small \cite{de2013phenetic}}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
  \begin{description}
  \item[NNF] negation normal form
  \item[d-DNNF] deterministic decomposable negation normal form
  \item[BDD] binary decision diagrams
  \item[SDD] sentential decision diagrams
  \item[$k$-Best] only use the $k$ most probable proofs
  \end{description}
\end{frame}

\begin{frame}{Example Diagrams for $C \land (A \lor \neg B)$}
  \vspace{-1em}
  % \begin{tikzpicture}
  %   \node[draw,circle] {$\land$}
  %   child {node[draw,rectangle] {$C$}}
  %   child {node[draw,circle] {$\lor$}
  %     child {node[draw,rectangle] {$A$}}
  %     child {node[draw,rectangle] {$\neg B$}
  %     }
  %   };
  % \end{tikzpicture}
  \begin{columns}[b]
    \begin{column}{0.33\textwidth}
      \begin{figure}
      \centering
        \begin{tikzpicture}
          \node[draw,circle] (A) {$A$}
          child {edge from parent[draw=none]}
          child {node[draw,circle] (B) {$B$} edge from parent[dashed]
            child {node[draw,circle,solid] (C) {$C$} edge from parent[dashed]
              child {node[draw,rectangle,solid] {$1$} edge from parent[solid]}
              child {node[draw,rectangle,solid] (0) {$0$}}
            }
            child {edge from parent[draw=none]}
          };
          \draw (A) -- (C);
          \draw (B) -- (0);
        \end{tikzpicture}
        \caption{BDD}
      \end{figure}
    \end{column}
    \begin{column}{0.34\textwidth}
      \begin{figure}
        \centering
        \begin{tikzpicture}
          \node[draw,circle] {$\land$}
          child {node[draw,circle] {$\lor$}
            child {node[draw,circle] (parent) {$\land$}
              child {node[draw,rectangle] {$B$}}
              child {edge from parent[draw=none]}
            }
            child {node[draw,circle] {$\land$}
              child {node[draw,circle] {$\lor$}
                child {node[draw,rectangle] (A) {$A$}}
                child {node[draw,rectangle] {$\neg A$}}
              }
              child {node[draw,rectangle] {$\neg B$}}
            }
          }
          child {node[draw,rectangle] {$C$}};
          \draw (parent) -- (A);
        \end{tikzpicture}
        \caption{d-DNNF}
      \end{figure}
    \end{column}
    \begin{column}{0.33\textwidth}
      \begin{figure}
        \centering
        \begin{tikzpicture}
          \tikzset{
            mysplit/.style={
              draw,
              rectangle,
              rectangle split,
              rectangle split horizontal,
              rectangle split parts=2
            }
          }
          \node[draw,circle] {$1$}
          child {node[mysplit] (bullet) {
              \nodepart{one} $\neg A$
              \nodepart{two}
            }
            child {node[draw,circle] (3) {$3$} edge from parent[draw=none]
              child {node[mysplit] {
                  \nodepart{one} $\neg B$
                  \nodepart{two} $C$
                }
              }
              child {node[mysplit] {
                  \nodepart{one} $B$
                  \nodepart{two} $0$
                }
              }
            }
          }
          child {node[mysplit] {
              \nodepart{one} $A$
              \nodepart{two} $C$
            }};
          \draw[*-] let \p1 = (bullet.two), \p2 = (bullet.center) in ({\x1 + 2.5},{\y2 + 2}) -- (3);
        \end{tikzpicture}
        \caption{SDD}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{What Characterizes a (Probabilistic) Logic Program?}
  \begin{columns}
    \hspace*{-0.7cm}\begin{column}{0.75\textwidth}
      \begin{empheq}[left =\onslide<6->{\color{color5}\empheqlbrace}]{equation}
        \begin{align*}
      \textcolor<5->{probability}{0.2} \prob &\textcolor<2->{predicate}{\mathtt{stress}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}). \\
      \textcolor<5->{probability}{0.3} \prob &\textcolor<2->{predicate}{\mathtt{influences}}(\textcolor<3->{variable}{\mathsf{P}_1}, \textcolor<3->{variable}{\mathsf{P}_2}) \ifff \textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<3->{variable}{\mathsf{P}_1}, \textcolor<3->{variable}{\mathsf{P}_2}). \\
      \textcolor<5->{probability}{0.1} \prob &\textcolor<2->{predicate}{\mathtt{cancer\_spont}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}). \\
      \textcolor<5->{probability}{0.3} \prob &\textcolor<2->{predicate}{\mathtt{cancer\_smoke}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{X}}) \ifff \textcolor<2->{predicate}{\mathtt{stress}}(\textcolor<3->{variable}{\mathsf{X}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{X}}) \ifff \textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{Y}}), \textcolor<2->{predicate}{\mathtt{influences}}(\textcolor<3->{variable}{\mathsf{Y}}, \textcolor<3->{variable}{\mathsf{X}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{cancer}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{cancer\_spont}}(\textcolor<3->{variable}{\mathsf{P}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{cancer}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \tikz \coordinate (start);\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{P}}), \textcolor<2->{predicate}{\mathtt{cancer\_smoke}}(\textcolor<3->{variable}{\mathsf{P}})\tikz \coordinate (end);. \\
                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{michelle}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{timothy}}). \\
                                         &\textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<4->{constant}{\mathit{timothy}}, \textcolor<4->{constant}{\mathit{michelle}}).
        \end{align*}
      \end{empheq}
    \end{column}
    \begin{column}{0.25\textwidth}
      \begin{itemize}
      \item[\textcolor{predicate}{\textbullet}]<2-> predicates, arities
      \item[\textcolor{variable}{\textbullet}]<3-> variables
      \item[\textcolor{constant}{\textbullet}]<4-> constants
      \item[\textcolor{probability}{\textbullet}]<5-> probabilities
      \item[\textcolor{color5}{\textbullet}]<6-> length
      \item[\textcolor{color6}{\textbullet}]<7-> complexity
      \end{itemize}
    \end{column}
  \end{columns}
  \onslide<7->{
    \begin{tikzpicture}[overlay]
      \draw [decorate,decoration={brace,amplitude=10pt,mirror},color=color6] (start) -- (end);
    \end{tikzpicture}
  }
\end{frame}

\begin{frame}{Clauses As Trees}
  \[
    \neg \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
    \lor (\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})
    \land \textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}}))
  \]
  \vfill
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \pause
      \centering
      \begin{tikzpicture}[level 1/.style={sibling distance=30mm},level 2/.style={sibling distance=15mm}]
        \node[draw,circle] {$\lor$}
        child {node[draw,circle] {$\neg$}
          child {node[draw,rectangle] {$\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$}}
        }
        child {node[draw,circle] {$\land$}
          child {node[draw,rectangle] {$\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$}}
          child {node[draw,rectangle] {$\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$}}
        };
      \end{tikzpicture}
    \end{column}
    \begin{column}{0.5\textwidth}
      \pause
      \centering
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        0 & 0 & 0 & 1 & 2 & 2 \\
        \hline
        $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ \\
        \hline
      \end{tabular}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Predicate Dependency Graph}
  \centering
  \begin{tikzpicture}
    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
    \draw[-{Latex[length=2mm]}] (person) -- (stress);
    \draw[-{Latex[length=2mm]}] (person) -- (spont);
    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
  \end{tikzpicture}
\end{frame}

\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{influences}}
    \independent \textcolor{predicate}{\mathrm{stress}}$}
  \centering
  \begin{tikzpicture}
    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
    \draw[-{Latex[length=2mm]}] (person) -- (stress);
    \draw[-{Latex[length=2mm]}] (person) -- (spont);
    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
    \draw<2->[-{Latex[length=2mm]}] (influences) edge[draw=red,bend left=15] (stress);
    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (influences);
    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
    \draw<2->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
  \end{tikzpicture}
\end{frame}

\begin{frame}{Stratification and Negative Cycles}
  \centering
  \begin{tikzpicture}
    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
    \draw[-{Latex[length=2mm]}] (person) -- (stress);
    \draw[-{Latex[length=2mm]}] (person) -- (spont);
    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
    \draw<2->[-{Latex[length=2mm]},draw=red] (smokes) -- (friend);
  \end{tikzpicture}
  \[
    \textcolor{probability}{0.1} \prob
    \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{X}},
    \textcolor{variable}{\mathsf{Y}}) \ifff
    \negg\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}).
  \]
\end{frame}

@@

% TODO: add a link to GitHub at the end
\begin{frame}{Summary}
%  \begin{itemize}
%  \end{itemize}
\end{frame}
